Overview

### 2023-06-09 README.Rmd
Remove Travis badge in README [no ci]

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/chainsawriot/oolong.svg?branch=master)](https://travis-ci.org/chainsawriot/oolong)
[![Codecov test coverage](https://codecov.io/gh/chainsawriot/oolong/branch/master/graph/badge.svg)](https://codecov.io/gh/chainsawriot/oolong?branch=master)
[![joss stataus](https://joss.theoj.org/papers/6e535564e7142d705f4f3d68b18dac62/status.svg)](https://joss.theoj.org/papers/6e535564e7142d705f4f3d68b18dac62)
[![CRAN status](https://www.r-pkg.org/badges/version/oolong)](https://CRAN.R-project.org/package=oolong)
[![R-CMD-check](https://github.com/chainsawriot/oolong/workflows/R-CMD-check/badge.svg)](https://github.com/chainsawriot/oolong/actions)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/chainsawriot/oolong/branch/master/graph/badge.svg)](https://codecov.io/gh/chainsawriot/oolong?branch=master)
[![joss stataus](https://joss.theoj.org/papers/6e535564e7142d705f4f3d68b18dac62/status.svg)](https://joss.theoj.org/papers/6e535564e7142d705f4f3d68b18dac62)
[![CRAN status](https://www.r-pkg.org/badges/version/oolong)](https://CRAN.R-project.org/package=oolong)
[![R-CMD-check](https://github.com/chainsawriot/oolong/workflows/R-CMD-check/badge.svg)](https://github.com/chainsawriot/oolong/actions)
[![R-CMD-check](https://github.com/chainsawriot/oolong/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/chainsawriot/oolong/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->
